%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{TrulyWP, Mavencart} % Job title
{Cloudineering} % Organization
{Chennai, India} % Location
{01. 2019 - 03.2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked in developing Golang server responsible for the creation, deletion and maintenance of Wordpress installs, using the client-go library to communicate with Kubernetes which will be present in each Google Kubernetes Engine cluster.}
\item {Worked in frontend server based on NodeJS from where users can create new WordPress installs.}
\item{Worked in developing the Kubernetes YAML files for system components and Wordpress components.}
\item{Worked in creating Dockerfiles for the Kubernetes deployments.}
\item{Used gRPC to communicate between system components for tasks like backup, housekeeping, bandwidth usage etc...}
\item {Implemented Prometheus for monitoring.}
\item{Used traefik as an edge router.}
\item{Worked in implementing OpenEBS based storage.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Maya, IOT, TCloud} % Job title
{Smartron} % Organization
{Chennai, India} % Location
{10. 2016 - 12. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Worked in developing an IOT application with nodeMCU WiFi microchip running on MongooseOS in mbedJS which connects to the Golang server using MQTT messaging. The Golang server saves the IOT data in Cassandra database and can deploy functions in Kubernetes based Serverless platform called Kubeless which runs the respective functions on pre-configured triggers.}
\item{Worked in fixing the sync of only parts of a large file that changed using librsync python library.}
\item{Worked in fixing the Windows icon overlay to show proper "sync, syncing, synced" status of a file syncing application using Python pywin32 library and Windows DLL in C++.}
\item{Developed a voice assistant/music search application's backend using azure cognitive service LUIS for intent and entity extraction with NodeJS as the language.}
\item{Worked in developing a proof of concept voice assistant client application using Raspberry Pi with trigger word detection and Google text to speech synthesis in python.}
\item{Worked in developing a proof of concept voice assistant client application using ESP8266 module using Lua and MQTT messaging protocol.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{MUDIS, Friend Locator} % Job title
{Inntot Technologies} % Organization
{Kochi, India} % Location
{8. 2015 - 8. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a TCP mock server in C for testing the Windows and Android client application being developed in the company.}
\item {Worked in the development of client to server communication of Windows client application in Visual C++ .}
\item{Developed the backend for a website using python-Django and MySQL.}
\item{Developed  "Know your election candidate" android application for 2016 Kerala elections.}
\item{Developed the backend for "friend locater" mobile application using python-Django and MySQL.}
\end{cvitems} 
}

%------------------------------------------------

\end{cventries}